Project Protocol

### 2019-10-22 protocol.Rmd
last modifications to results, outcomes, ...

Plots will be made in R~[@RCore], with the `ggplot2` package~[@ggplot2].

@@

Computation will be done using R~[@RCore], with the `lme4` package~[@lme4].

@@

#	Resources
This work will be supported by ACEMS funding - $500 to pay 100 participants equally.

#	Results, outcomes and future plans
 - Plans for return of results of research to participants
 - Publication plan
 - Other potential uses of the data at the end of the project
 - Project closure processes 
 - Plans for sharing and/or future use of data and/or follow-up research

>>>>

Plots will be made in R [@RCore], with the `ggplot2` package [@ggplot2].

@@

Computation will be done using R [@RCore], with the `lme4` package [@lme4].

@@

#	Resources

Each participant will earn $AUD5 for their work.

#	Results, outcomes and future plans

## Plans for return of results of research to participants

There is no intention to provide the results to participants. This might compromise their ability to participate in future experiments.

## Publication plan

We intend to publish this work as a research article in a top journal, along with de-identified data as required by the journal's reproducibility policy.

## Other potential uses of the data at the end of the project

We do not intend to re-use this data, we don't see any major reasons for others to use this data. It may be possible that the data may be aggregated with many other studies to examine effects of education, age and gender on reading data plots.

## Project closure processes

The project will be closed once the journal article is published.

## Plans for sharing and/or future use of data and/or follow-up research

Details are provided in the Data Management Plan. The results from this study might inform design of future studies.
